\input{../header}

\begin{document}

\section{Health and Safety Policy}

This is the statement of general policy and arrangements for Electromagnetic Field Ltd (EMF).

EMF is an entirely volunteer-run organisation and does not employ any staff. Consequently, many statutory responsibilities for employers in health \& safety law do not apply. EMF does have a statutory duty for the health and safety of volunteers and contractors under section 4 of the Health and Safety At Work etc. Act 1974.

EMF will voluntarily comply with all appropriate health \& safety legislation to ensure events run to a high standard of safety.

Overall and final responsibility for health \& safety is that of Russell Garrett.
Day-to-day responsibility for ensuring this policy is put into practice is delegated to the appropriate team leads.

\tabulinesep=2mm
\begin{tabu}{| p{7cm} | p{3cm} | p{5cm} |} \hline
  \rowfont{\bfseries} Statement of general policy & Responsibility of & Action/Arrangements \\ \hline
To prevent accidents and cases of work-related ill health and provide adequate control of health and safety risks arising from work activities & Russell Garrett & Risk assesment to be completed in Event Management Plan, and reviewed per event, with actions arising implemented. First aid incident statistics to be reviewed after each event. \\ \hline
To provide adequate training to ensure volunteers are competent to do their work & Team Leads & Volunteers to be given training where necessary. \\ \hline
To engage and consult with volunteers on day-to-day health and safety conditions and provide advice and supervision on occupational health & Russell Garrett, Team Leads & Volunteers to be encouraged to report health and safety concerns. \\ \hline
To implement emergency procedures and evacuation in case of fire or other significant incident. & Russell Garrett & Emergency plans will be documented and included in the event management plan. Stewards to be advised on emergency procedures before they start work. \\ \hline
To maintain safe and healthy working conditions, provide and maintain plant, equipment and machinery, and ensure safe storage / use of substances & Team Leads & Regular inspections of site and facilities safety. Rented equipment to come from reputable suppliers. \\ \hline
\end{tabu}

First aid cover is provided by the first aid team, who will record incidents in their patient reporting system.

Policy last updated by Russell Garrett on 2019/02/12. This policy is subject to review and revision before each event.
\end{document}
